Best Practices for Alchemical Free Energy Calculations [Article v\versionnumber]

### 2024-07-12 paper/manuscript.tex

Many choices of restraints involve selecting reference atoms.
Again, in principle this choice is unimportant given adequate simulation time but practical considerations may be important.
The choice is likely especially important with Boresch-style restraints, where some relative placements of reference atoms are likely to be numerically unstable; additionally, ligand reference atoms should likely be in a part of the molecule which defines the binding orientation well, rather than in a floppy solvent-exposed tail, for example.

>>>>

Many choices of restraints involve selecting reference atoms.
Again, in principle this choice is unimportant given adequate simulation time but practical considerations may be important.
The choice is likely especially important with Boresch-style restraints, where some relative placements of reference atoms are likely to be numerically unstable; additionally, ligand reference atoms should likely be in a part of the molecule which defines the binding orientation well, rather than in a floppy solvent-exposed tail, for example. Several automated methods have been proposed to select anchor points for Boresch restraints, which typically involve analysing a simulation of the fully-interacting receptor-ligand complex~\cite{alibay2022evaluating, alibay2021mdrestraintsgenerator, baumann2023broadening, chen2023enhancing, hedges2023suite}.
